A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-18 writeup/paper.tex
Removed natbib

\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage[numbers]{natbib}
\usepackage[fit]{truncate}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{multirow}
\usepackage{dblfloatfix}
\usepackage{float}
\usepackage{subfigure}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{5.4cm}    % Expanding the titlebox

@@

As the use of MTurk has grown, researchers have become interested in who exactly makes up the Turker population. Early demographic studies by \newcite{ipeirotis:2010:demographics} revealed that Turkers are typically younger and more educated than the population as a whole. The study found that while most Turkers cite money as a motivation for working on MTurk, few cite it as their only motivation. A follow-up study by Ross et al. found that the majority of Turkers were located in the US, 30\% of Turkers were located in India, and that Indian Turkers tend to have lower incomes than US-based Turkers. Ross et al. also suggested that the international presence on MTurk has been growing over time. While there has not yet been a thorough investigation of Turkers' language abilities, Munro compiled survey responses of 2,000 Turkers, revealing that four of the six most represented languages come from India (the top six being Hindi, Malayalam, Tamil, Spanish, French, and Telugu). No study has yet been conducted to comprehensively assess the language skills of the growing number of international and bilingual Turkers or to analyze the potential of MTurk to support work in low-resource languages.

>>>>

\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage[fit]{truncate}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{multirow}
\usepackage{dblfloatfix}
\usepackage{float}
\usepackage{subfigure}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{5.4cm}    % Expanding the titlebox

@@

As the use of MTurk has grown, researchers have become interested in who exactly makes up the Turker population. Early demographic studies by \newcite{ipeirotis:2010:demographics} revealed that Turkers are typically younger and more educated than the population as a whole. The study found that while most Turkers cite money as a motivation for working on MTurk, few cite it as their only motivation. A follow-up study by Ross et al. found that the majority of Turkers were located in the US, 30\% of Turkers were located in India, and that Indian Turkers tend to have lower incomes than US-based Turkers. Ross et al. also suggested that the international presence on MTurk has been growing over time. While there has not yet been a thorough investigation of Turkers' language abilities, \newcite{munro-tily:2011} compiled survey responses of 2,000 Turkers, revealing that four of the six most represented languages come from India (the top six being Hindi, Malayalam, Tamil, Spanish, French, and Telugu). No study has yet been conducted to comprehensively assess the language skills of the growing number of international and bilingual Turkers or to analyze the potential of MTurk to support work in low-resource languages.
